Stochastic Gradient Descent

### 2018-04-29 sgd/sgd.tex
wek
werk

	Parametric assumptions can make this optimization very nice \\~\\

@@

\begin{frame}
	\frametitle{SGD is very popular in academia and industry}
	Many, many statistical learning models use SGD to fit weights \\~\\

@@

	Example: Google's \textbf{AlphaGo} program.
\end{frame}

\begin{frame}
	\begin{figure}[b]
	\centering
	\includegraphics[scale=0.4]{go}
	\end{figure}
\end{frame}

>>>>

	Parametric assumptions can make this optimization ``nice'' \\~\\

@@

\begin{frame}
	\frametitle{SGD is very popular in academia and industry}
	Many, many, \textit{many} statistical learning models use SGD to fit weights \\~\\

@@

\begin{frame}
	\frametitle{Example: Google's \textbf{AlphaGo} program}
	\begin{figure}[b]
	\centering
	\includegraphics[scale=0.4]{go}
	\end{figure}
\end{frame}
